Defining properties regulating pioneer-factor binding and function

### 2022-11-21 manuscript/manuscript.qmd
update results
update results section

---
title: "Defining properties regulating pioneer-factor binding and function"
format: html
editor: visual
bibliography: references.bib
---

@@

-   Establish system for ectopic expression of pioneer factors

-   Identification of physiological expression levels

@@

To determine how exogenous Zld and Grh interact with preexisting chromatin in S2 cells, we expressed each factor at physiological levels and determined genome-wide binding sites using chromatin immunoprecipitation coupled with sequencing (ChIP-seq). We identified XXXX peaks for Zld and XXXX for Grh.

@@

**Extended data Figure 1: Stable cell lines allow inducible expression of transcription factors at physiological concentrations.**

@@

-   Schematic of stable cell line generation.

-   Cell line validation by RNA-seq

-   Verification of protein expression.

-   Determination of physiological protein levels.

-   QC for genomics datasets: e.g. PCA, replicate correlation, example genome browsers of individual replicates.

-   Antibody controls: IgG, IPs in WT cells, etc.

-   CUT&RUN time course for Zld and Grh?

@@

-   GO analysis for RNA-seq data

-

>>>>

---
title: "Defining properties regulating pioneer-factor binding and function"
format: html
editor: visual
bibliography: references.bib
#csl: nature.csl
---

@@

-   ~~Establish system for ectopic expression of pioneer factors~~

-   ~~Identification of physiological expression levels~~

@@

To determine how exogenous Zld and Grh interact with preexisting chromatin in S2 cells, we expressed each factor at physiological levels and determined genome-wide binding sites using chromatin immunoprecipitation coupled with sequencing (ChIP-seq). We identified XXXX peaks for Zld and XXXX for Grh. To control for antibody specificity, we performed additional ChIP experiments using IgG, anti-Zld, or anti-Grh (Extended Data Fig. XX). We excluded any peaks that were called in these datasets, ensuring that we analyzed peaks that were detected only upon ectopic expression of Zld or Grh. <!--# Not sure the best way to discuss the control ChIP experiments. Should I mention how many peaks we detect in WT cells? What supplemental figures should I include? Should peak calling be done using IgG or WT cells as control instead of input? -->

Having established that Zld and Grh can bind to thousands of sites in S2 cells, we performed ATAC-seq on WT cells or cells expressing Zld or Grh to determine if these factors bind and open closed chromatin in S2 cells. We performed differential accessibility analysis comparing Zld or Grh-expressing cells to WT cells. We detected XXX differentially accessible regions for Zld and XXX for Grh.

@@

**Extended Data Figure 1: Stable cell lines allow inducible expression of transcription factors at physiological concentrations.**

-   Schematic of cell line generation.

-   RNA-seq data to show expression of S2 and not Kc cell markers.

-   Western blots to determine physiological expression and lack of protein expression in WT cells.

-   RNA-seq data to show leaky expression and strong induction of RNA levels.

**Extended Data Figure 2: Ectopically expressed Zld and Grh bind to thousands of sites in S2 cells.**

-   ChIP-seq replicate correlation

-   Genome browser and heatmaps for all ChIP peaks?

-   IgG and WT controls for antibody specificity

**Extended Data Figure 3: Ectopic expression of pioneer factors in S2 cells leads to widespread changes to chromatin accessibility.**

-   ATAC PCA plot

-   ATAC replicate correlation

-   volcano and/or MA plots with enrichment of binding

-   Example genome browsers?

-   Analysis of nonspecific changes?

**Extended Data Figure 4: Zld and Grh bind to chromatin rapidly after induction of protein expression**

-   CUT&RUN time course to show rapid binding

-   likely rules out dependence on DNA replication

**Extended Data Figure 5: Zld and Grh binding promotes transcriptional activation at a subset of binding sites**

-   RNA-seq PCA

-   RNA-seq replicate correlation

-   RNA-seq volcano/MA plots

-   RNA-seq GO analysis

@@

@@
